Douglas-Complex Fire PM2.5

### 2018-06-06 r_scripts/analysis/wfs_exposure_figures.Rmd
Updated exposure figures to go in paper.

# save figure
ggsave(filename = "./r_scripts/analysis/Figs/smoke_map.tiff", plot = smoke_map,
       units="in", width=6, height=5, dpi=300)
```

@@

# small multiples plot
plot <- ggplot(county_pm_df, aes(x=date, y= geo_smk_pm)) + 
geom_point(color = "#6a3093", size = 0.5) +
scale_x_date(date_labels = "%m") +
geofacet::facet_geo(~county, grid = or_grid) +
ylab(expression("Smoke PM2.5 ?g/m"^3)) +
xlab("Month in 2013") +
theme(panel.background = element_rect(fill = 'white', colour = 'black'),
strip.text = element_text(size = 8),
panel.grid.major = element_blank(),
panel.grid.minor = element_blank(),
strip.background = element_rect(colour=NA, fill=NA),
legend.position = "bottom")
# plot 
plot
# save figure
ggsave(filename = "./county_smoke_timeseries.png", plot = plot)
```

>>>>

# save figure
 ggsave(filename = "./r_scripts/analysis/Figs/smoke_map.tiff", plot = smoke_map,
        units="in", width=7, height=6, dpi=300)
```

@@

# small multiples plot
plot <- ggplot(county_pm_df, aes(x=date, y= geo_smk_pm)) + 
  geom_point(color = "#6a3093", size = 0.5) +
  #scale_x_date(date_breaks = "1 month", labels = "%b") +
  geofacet::facet_geo(~county, grid = or_grid) +
  ylab(expression(paste("Wildfire Smoke PM"[2.5], " µg/m"^3))) +
  xlab("2013 Wildfire Season") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.text = element_text(size = 8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA),
    legend.position = "bottom",
    axis.text.x = element_text(angle = 90, hjust = 0.5, vjust = 0))
# plot 
plot
# save figure
# ggsave(filename = "./r_scripts/analysis/Figs/county_smoke_timeseries.tiff", 
#        plot = plot, units="in", width=6, height=5, dpi=300)
```
